%-----------------------------------------------------------------------------------------------------------------------------------------------%
%	The MIT License (MIT)
%
%	Copyright (c) 2021 Jitin Nair
%
%	Permission is hereby granted, free of charge, to any person obtaining a copy
%	of this software and associated documentation files (the "Software"), to deal
%	in the Software without restriction, including without limitation the rights
%	to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%	copies of the Software, and to permit persons to whom the Software is
%	furnished to do so, subject to the following conditions:
%	
%	THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%	IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%	FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%	AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%	LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%	OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
%	THE SOFTWARE.
%	
%
%-----------------------------------------------------------------------------------------------------------------------------------------------%

%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,12pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}


% job listing environments
\newenvironment{jobshort}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    }
    {
    }

\newenvironment{joblong}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
    }
    {
    \end{itemize}
    \end{minipage}    
    }

\bibliography{citations.bib}

%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{CV of Ir. Rafael Malach Dulfer, MSc} \\[7.5pt]
\end{tabularx}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

%Interests/ Keywords/ Summary
\section{Interests}
\begin{itemize}
\item Programming Language Design
\item Automation
\item Software Architecture
\item Modernizing
\item Open-Source
\end{itemize}

\section{Skills}
\begin{multicols}{2}
\begin{itemize}
    \item Programming Languages:
        \begin{itemize}
            \item Python
            \item PHP
            \item Rust
            \item Java
            \item Haskell
            \item JavaScript
            \item SQL
        \end{itemize}
    \item Natural Languages:
        \begin{itemize}
            \item Dutch
            \item English
        \end{itemize}
    \item Linux
    \item Server Hosting
    \item Git
    \item Scrum
\end{itemize}
\end{multicols}

%Experience
\section{Work Experience}

\begin{joblong}{Web Developer - Netherlands Society of Cinematography}{Jan 2023 - Now}
\item Took over development from previous developer and streamlined backend to simplify the addition of new features and added new features as required.
\item Also increased page load speed by up to 3x on some pages and fixed security issues.
\item \href{https://cinematography.nl}{cinematography.nl}
\end{joblong}

\begin{jobshort}{Software Development - BRBA}{Feb 2021 - Jul 2021}
From February to July 2021 I was part of the \href{https://www.ronroozendaal.nl/blog/2021/05/een-nieuw-registratiesysteem-in-een-paar-weken-tijd}{BRBA} team working on vaccination registration software for the Dutch Ministry of Health Welfare and Sport (MinVWS) on tasks ranging from validation+encryption, integration testing and the streamlining of build processes.
\end{jobshort}

\begin{joblong}{Web Developer - Anubis}{Jan 2021 - Apr 2022}
\item Developed an online examination system for the University of Twente in use by the courses `Network Systems' and `Web Science'.
\item Self-designed Markdown dialect + parser to define the structure of exams 
\item Over 100 students load and use the system at the same time, with a low tolerance for failure. 
\end{joblong}

\begin{jobshort}{Software Development - Serious Game Automatisering}{Jun 2019 - Aug 2019}
Was commissioned by De Winter Information Solutions to create a dedicated interface to streamline and partially automate the ``hosting'' of a serious game for the Association of Dutch Municipalities (VNG).
\end{jobshort}

\section{Extracurriculars}
\begin{itemize}
    \item Volunteer work at various cultural spaces and events.
    \item Managing the band rehearsal rooms of the University of Twente.
    \item Organizing multiple jam and band nights.
\end{itemize}
  
%Projects
\section{Projects}

\begin{tabularx}{\linewidth}{ @{}l r@{} }

\textbf{Mr Kite's Maginificent Kut-Up Machine} & \hfill \href{https://mkmkm.thebias.nl}{Stream} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{An infinite audio stream that takes a large database of music, shuffles it, manipulates it, cuts it up and glues it back together to play in short fragments. Written in Python (+ QT for the local \href{https://github.com/Rafaeltheraven/Mr-Kite-s-Magnificent-Kut-up-Machine}{GUI} version).}  \\

\textbf{Nethacklang} \\
\multicolumn{2}{@{}X@{}}{Parser + Compiler for an esolang inspired by the game Nethack, in which a developer must design a level as well as a player agent that interacts with the environment in order to do I/O. Written in Haskell.} \\

\textbf{WAGon} & \hfill \href{https://wagon.thebias.nl/}{Documentation} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{My Master's Thesis Project was a DSL to define Weighted Attribute Grammars, an ecosystem to use this DSL and a GLL-based parser generator to show how to use it. Written in Rust. \newline Final grade 9.0.} \\

\textbf{The Propaganda Machine} & \hfill \href{https://ieee-cog.org/2021/assets/papers/paper_231.pdf}{Paper} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{My Bachelor's Thesis Project was to develop a program that automatically writes propaganda pieces based on a game of Risk. Undertook research on the effectiveness of simple automatically generated propaganada. Written in Python + Java. \newline Final grade 8.0.} \\

\end{tabularx}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}}	
2021 - 2024 & MSc, Software Technology\hfill \textbf{University of Twente} \\

2017 - 2021 & BSc, Technical Computer Science\hfill \textbf{University of Twente} \\ 

2019 - 2020 & Minor New Media Language\hfill \textbf{Kaunas University of Technology} \\

2018 - 2019 & BSc of Honours, Philosophy\hfill \textbf{University of Twente} \\

2014 - 2017 & IB English A Language \& Literature \hfill \textbf{Het Berlage Lyceum} \\

2017 & VWO E\&M \hfill \textbf{Het Berlage Lyceum} \\

2015 & Summer Course Computer Science \hfill \textbf{Oxford University} \\

2014 & Junior TTO Certificate \hfill \textbf{Cambridge Education Group} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------
\section{Publications}
\begin{refsection}[citations.bib]
\printbibliography[heading=none]
\nocite{*}
\end{refsection}

\section{Contact Details}
\begin{tabularx}{\linewidth}{@{} C @{}}
\href{https://github.com/rafaeltheraven}{\raisebox{-0.05\height}\faGithub\ Rafaeltheraven} \ $|$ \ 
\href{https://linkedin.com/in/rafael-dulfer-b60a32111/}{\raisebox{-0.05\height}\faLinkedin\ Rafael Dulfer} \ $|$ \ 
\href{https://dulfer.be}{\raisebox{-0.05\height}\faGlobe \ dulfer.be} \ $|$ \ 
\href{mailto:rafael@dulfer.be}{\raisebox{-0.05\height}\faEnvelope \ rafael@dulfer.be} \ $|$ \ 
\href{tel:+31616935305}{\raisebox{-0.05\height}\faMobile \ +316.169.353.05} \\
\end{tabularx}

\end{document}
